### 2018-03-16 paper.Rmd
knit settings

```{r load_packages, include = FALSE}
library(papaja)
library(tidyverse)
library(childesr)
library(directlabels)
knitr::opts_chunk$set(cache = TRUE)
```

>>>>

```{r load_packages, echo = FALSE}
library(papaja)
library(tidyverse)
library(childesr)
library(directlabels)
knitr::opts_chunk$set(cache = TRUE, echo = FALSE)
```
